Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-01 EconGrowth.Rnw
Now doing str(dataTable) to see what is going on inside the data.frame.

<<CD_Params_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) model parameters.">>=
createCDParamsGraph <- function(){
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", 
                       lapply(countryAbbrevs, 
                              cobbDouglasCountryRowsForParamsGraph))
  print(class(dataTable))
  print(dataTable)
  # Make a graph. I want the following:
  ### two-letter country abbreviation on the horizontal axis
  ### dots for the values of each parameter
  ### error bars to the top and bottom of the dots representing the 95% CI
  ### three panels, one for each parameter (lambda, alpha, and beta)
  #
  # Note that "segplot" is in the "latticeExtra" package.
  # But, at this point, I obtain the following error:
  # "Error:  range not meaningful for factors"
  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable, 
                   centers = value)
  return(graph)
}
createCDParamsGraph()
@

>>>>

<<CD_Params_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) model parameters.">>=
createCDParamsGraph <- function(){
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", 
                       lapply(countryAbbrevs, 
                              cobbDouglasCountryRowsForParamsGraph))
  print(class(dataTable))
  print(dataTable)
  print(str(dataTable))
  # Make a graph. I want the following:
  ### two-letter country abbreviation on the horizontal axis
  ### dots for the values of each parameter
  ### error bars to the top and bottom of the dots representing the 95% CI
  ### three panels, one for each parameter (lambda, alpha, and beta)
  #
  # Note that "segplot" is in the "latticeExtra" package.
  # But, at this point, I obtain the following error:
  # "Error:  range not meaningful for factors"
  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable, 
                   centers = value)
  segplot(reorder(factor(county), rate.male) ~ LCL95.male + UCL95.male, 
          data = subset(USCancerRates, state == "Washington"), 
          draw.bands = FALSE, 
          centers = rate.male)
  return(graph)
}
createCDParamsGraph()
@
